### 2018-07-16 paper/related.tex
started adding to related work, with p2p storage, p2p onion routing, etc.

@@

@@

There is a concern shared with traditional p2p file sharing, namely churn~\cite{dhtchurn} and its effect on availability - here in the narrow context of the set of user devices based on user behavior. We thus discuss the related work on predicting device availability next, though to the best of our knowledge we are the first to make use of such predictions to cope with churn in interoperating sets of user devices.

>>>>

As a whole, \name is related to but differs from the following concepts: storage and sharing (cloud, P2P file sharing, P2P storage),  mixnets, and onion routing (with infrastructure or P2P).

@@

There have been several attempts at P2P storage, mostly for backup. Wuala, Farsite, Nebulostore.
\sonja{will expand and cite}

There is a concern shared with traditional P2P file sharing, namely churn~\cite{dhtchurn} and its effect on availability - here in the narrow context of the set of user devices based on user behavior. We thus discuss the related work on predicting device availability next, though to the best of our knowledge we are the first to make use of such predictions to cope with churn in interoperating sets of user devices.

@@

Onion routing, with infrastructure and governance (Tor) and without (I2P), are geared toward web browsing. \sonja{will expand and cite}

\sonja*{include some on Modeling devices' connection and disconnection}
